### 2021-10-28 manuscript/hiv-gwas.tex

\begin{figure}
\includegraphics[width = 0.3\linewidth]{figures/pathogen_tree_with_trait.png}
\includegraphics[width = 0.3\linewidth]{figures/pathogen_tree_with_phylo-estimated_env_trait.png}
\includegraphics[width = 0.3\linewidth]{figures/pathogen_tree_with_phylo-estimated_pathogen_trait.png}
	\caption{Inferred viral phylogeny with tips colored by measured total spVL, estimated non-viral part of spVL, and estimated viral part of spVL.}
	\label{fig:spvl-on-tree}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width = 0.3\linewidth]{figures/spvl_on_tree.png}
	\caption{Inferred HIV-1 $pol$ gene phylogeny with tips colored by calculated spVL and estimated pathogen and non-pathogen parts of spVL.}
	\label{fig:spvl-on-tree}
\end{figure}
